Bare minimum: set theory

### 2021-05-26 BareMinima/SetTheory/BareMinimumSetTheory.tex
BM-SetTheory: added image for partitions

\begin{remark}
	Ordered pairs and disjoint unions exemplify the effort in set theory to construct \emph{all objects} starting from just two primitives: set and set inclusion. The downside is that the constructions do not map exactly to our intuition. For example, we still think an ordered pair as a set, so we want to write $b \in (a, b)$, though, looking at the definition $b$ itself is not directly a member of $(a, b)$.
\end{remark}

@@

\begin{remark}
	Relations provide a common foundation for functions (i.e. the relation is the set of pairs $(x, f(x))$ ), equivalences and order (i.e. the relation is the set of pairs $(a, b)$ such that $a=b$ or $a\leq b$ respectively). This exemplifies the effort in set theory to find general structures.
\end{remark}

@@

}
\begin{defn}[Binary relation]
	Given a set $A$, \marginleft{Binary\\ relation: $aRb$} called \textbf{domain}, and a set $B$, called \textbf{codomain}, a \textbf{binary relation} is a set $R \subseteq A \times B$ of ordered pairs. We say $a$ is \textbf{$R$-related} to $b$, noted $aRb$ if $(a,b) \in R$. If $A=B$ (i.e. domain and codomain coincide) the relation is said to be \textbf{homogeneous}, \textbf{heterogeneous} if not.
\end{defn}

@@

\begin{defn}[Partitions]
	A \textbf{partition} \marginleft{Partitions} of a set $A$ is a collection $P \subset \mathcal{P}(A)$ of disjoint subsets that cover all of $A$. That is:
	\begin{enumerate}
		\item $\bigcup\limits_{B \in P} B = A$
		\item $B \cap C = \emptyset$ for all $B, C \in P$ where $B \neq C$
	\end{enumerate}
\end{defn}

@@

TODO: diagram

>>>>

\begin{remark}
	Ordered pairs and disjoint unions exemplify the effort in set theory to construct \emph{all objects} starting from just two primitives: set and set inclusion. The downside is that the constructions do not map exactly to our intuition. For example, we still think as an ordered pair as a set, so we want to write $b \in (a, b)$, though, looking at the definition $b$ itself is not directly a member of $(a, b)$.
\end{remark}

@@

@@

}
\begin{remark}
	Relations provide a common foundation for functions (i.e. the relation is the set of pairs $(x, f(x))$ ), equivalences and order (i.e. the relation is the set of pairs $(a, b)$ such that $a=b$ or $a\leq b$ respectively). This exemplifies the effort in set theory to find general structures.
\end{remark}

\begin{defn}[Binary relation]
	Given a set $A$, \marginleft{Binary\\ relation: $aRb$} called \textbf{domain}, and a set $B$, called \textbf{codomain}, a \textbf{binary relation} is a set $R \subseteq A \times B$ of ordered pairs. We say $a$ is \textbf{$R$-related} to $b$, noted $aRb$ if $(a,b) \in R$. If $A=B$ (i.e. domain and codomain coincide) the relation is said to be \textbf{homogeneous}, \textbf{heterogeneous} if not.
\end{defn}

@@

\marginright{~\\
	\def\setA{ (0,0) ellipse (5 and 4) }
	\begin{tikzpicture}[scale = 0.3]
		\draw \setA;
		\begin{scope}
			\clip \setA;
			\draw (-5, 4) .. controls (0, 2) and (0, -2) .. (-5, -4);
			\draw (2, 4) .. controls (2, 2) and (0, 1) .. (-1.46, 1);
			\draw (1, 1.9) .. controls (1.5, 1) and (2, -2.5) .. (0.5, -4);
			\draw (1.49, -1)  .. controls (2, -0.3) and (4, 0.5) ..  (5, 0);
		\end{scope}
		\node at (-4, -4.5) {$A$};
		\node at (-3.2, 0) {$P_1$};
		\node at (-0.4, 2.6) {$P_2$};
		\node at (-0.2, -1.2) {$P_3$};
		\node at (3, -1.7) {$P_4$};
		\node at (3, 1.5) {$P_5$};
	\end{tikzpicture} 
}
\begin{defn}[Partitions]
	A \textbf{partition} \marginleft{Partitions} of a set $A$ is a collection $P \subset \mathcal{P}(A)$ of disjoint subsets that cover all of $A$. That is:
	\begin{enumerate}
		\item $\bigcup\limits_{B \in P} B = A$
		\item $B \cap C = \emptyset$ for all $B, C \in P$ where $B \neq C$
	\end{enumerate}
\end{defn}

@@
